---
title: "Select"
tutorial:
  id: "rwdir-learnr/select"
  version: .9
output:
  learnr::tutorial:
    progressive: true
    theme: lumen
    highlight: espresso
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

This is a work in progress. The goal is to write an example **learnr** lesson for Reporting with Data in R. This is just a draft concept.


## Learn the Force: Select

Explain concepts using Star Wars data.

The [select]() function lets you pick columns.

### Select columns

You want to:

- select specific columns in your data
- drop specific columns in your data

## Use the Force: Select

First, look at the columns available

```{r select-intro, exercise = T}
starwars %>% glimpse()
```

### Select specific columns

Use [select]() when you want to select specific columns from your data.

```{r select-select, exercise = T}
starwars %>% 
  select(name, sex, homeworld)
```


In this case you specify exactly the columns of data that you need. In this case we want:


### Drop a specific column

```{r select-drop, exercise = T}
starwars %>% 
  select(-c(films, vehicles, starships))
```



## Scoobydoo

- Data from [TidyTuesday, 2021-07-13,  Scooby-doo](https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-07-13/readme.md)
- About [Scooby-doo Complete](https://www.kaggle.com/williamschooleman/scoobydoo-complete)

```{r import-scoobydoo, message=FALSE, warning=FALSE, include=FALSE}
# scoobydoo <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-07-13/scoobydoo.csv')
# scoobydoo %>% write_csv("data/scoobydoo.csv")

scoobydoo <- read_csv("data/scoobydoo.csv")
scoobydoo %>% glimpse()
```

## Crime stats

- [Crime Reports About the data](https://data.austintexas.gov/Public-Safety/Crime-Reports/fdj4-gpfu)
- Export is export of 2021 data only (downloaded 1/2/2022)

```{r import-crime, include=FALSE}
crime <- read_csv("data/atx-crime-2021.csv") %>% janitor::clean_names()
crime %>% glimpse()
```






