---
title: "J327D Do Now: Summarizing by Count"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
#library(gradethis)

starwars <- starwars
```

Hello again! In this exercise, you'll be practicing the `summarize()` and `group_by()` functions that you learned in Chapter 3 and 4 of [our textbook](https://utdata.github.io/rwdir/counts-import.html). Like our previous exercise, we'll be using the dataset `starwars` in the `tidyverse` packages.

## Summarizing

If you recall from our earlier exercise, `starwars` is a dataset with 87 Star Wars characters.

```{r glimpse}
glimpse(starwars)
```

What if we wanted to *group* the characters by `species` and count them? What two functions would we use?
```{r gbsumexercise, exercise = TRUE}
starwars
```

```{r gbsumexercise-solution, exercise.reveal_solution = FALSE}
starwars %>%
  group_by(species) %>%
  summarize(count = n())
```

<div id="gbsumexercise-hint">
**Hint:** Check out the `group_by()` and `summarize()` in [Chapter 4](https://utdata.github.io/rwdir/count-analysis.html#summarize)
</div>

## Arrange

While the `group_by()` and `summarize()` functions are great for getting this information, the information is not ordered. What function would we use to **arrange** this data?

As a tip, don't forget that we often want to sort the information by **desc**ending order, because journalists are typically interested in the *most* of something. 
```{r arrangeexercise, exercise = TRUE}
starwars %>%
  group_by(species) %>%
  summarize(count = n())
```

```{r arrangeexercise-solution, exercise.reveal_solution = FALSE, include = FALSE}
starwars %>%
  group_by(species) %>%
  summarize(count = n()) %>%
  arrange(count %>% desc())
```

<div id="arrangeexercise-hint">
**Hint:** Check out `arrange` in [Chapter 4](https://utdata.github.io/rwdir/count-analysis.html#arrange-the-results)
</div>

```{r quiz-arrange, include = FALSE}
quiz(
  question("What species is the most common in Star Wars",
    answer("Human", correct = TRUE),
    answer("Droid"),
    answer("Aleena"),
    answer("Iktotchi")
  )
)
```
