---
title: "J327D Week 1C: Working Directory"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
```

## Working Directory

Okay! So now you know what objects and functions are, and you know how to install packages. Let's talk about your Working Directory.

In most cases, you want to import data from your computer into the R environment. This requires you to know where your R file is and to understand how to import it. The folder your R file is in is usually your working directory.

You can use the function `getwd()` to figure out the working directory you are in. 

```{r 11th, exercise = TRUE}
getwd()
```

You can set the working directory using the `setwd()` function, or by going to Session --> Set Working Directory. `setwd()` takes the a folder directory string as an argument, like `"C:/Users/lukitoputer/Documents/2021F_J327D"`. 
```{r, eval = FALSE}
setwd()
```

## Mastering Working Directory
```{r quiz-wd, echo=FALSE}
quiz(
  question("What function would you use to figure out your working directory folder?",
    answer("getwd()", correct = TRUE),
    answer("setwd()"),
    answer("library()"),
    answer("str()")
  )
)
```


