---
title: "J327D Do Now: Tidyverse"
output: 
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(gradethis)

starwars <- starwars
```

In this exercise, you'll be practicing the `tidyverse` skills that you learn this week! To practice, we'll be using a dataset called `starwars`, which can be loaded in with the `tidyverse` package.

## 1:Previewing our data

First, let's learn about the `starwars` dataset. What function would you use to *glimpse* at the data?

```{r glimpseexercise, exercise = TRUE}

```

```{r glimpseexercise-solution, exercise.reveal_solution = FALSE, include=FALSE}
glimpse(starwars)
```

<div id="glimpseexercise-hint">
**Hint:** Check out the `glimpse()` function, which we talk about in [Chapter 3](https://utdata.github.io/rwdir/counts-import.html#glimpse-the-data)
</div>


```{r quiz-glimpse, echo=FALSE, include=FALSE}
quiz(
  question("How many Star Wars characters are in the dataset",
    answer("14"),
    answer("87", correct = TRUE),
    answer("41"),
    answer("Unknown")
  )
)
```

## 2:Focusing on variables

Let's say we want to *select* only on the following variables: `name`, `height`, `homeworld`, and `species`. How do we do that?

```{r selectexercise, exercise = TRUE}

```

<div id="selectexercise-hint">
**Hint:** I recommend checking out the `select()` function, which we talk about in [Chapter 3](https://utdata.github.io/rwdir/counts-import.html#selecting-columns)
</div>

```{r selectexercise-solution, exercise.reveal_solution = FALSE, include=FALSE}
starwars %>%
  select(
    name,
    height,
    homeworld,
    species
  )
```

```{r arrangeexercise-setup, include=FALSE}
starwars <- starwars %>%
  select(
    name,
    height,
    homeworld,
    species
  )
```

## 3:Arranging our Data

Now that we have *glimpse*d our data and *select*ed our variables of interest, let's *arrange* them using by height. How do we do that?
```{r arrangeexercise, exercise = TRUE}

```

```{r arrangeexercise-solution, exercise.reveal_solution = FALSE, include = FALSE}
starwars %>%
  arrange(-height)
```

```{r quiz-arrange, include = FALSE}
quiz(
  question("Who is the tallest character?",
    answer("Yoda"),
    answer("Darth Vader"),
    answer("Chewbacca"),
    answer("Yarael Poof", correct = TRUE)
  )
)
```
